---
title: Time Series Minimum Wage Studies Meta-Analysis - Presentation
output: 
  beamer_presentation: 
    theme: Warsaw
    colortheme: lily
author: Gabriele Stella, Weida Pan, Karan Kashyap
date:      June, 2022
fontsize:  9 pt  
---


```{r}
load('Data/Environment.Rdata')
```



## Introduction

- our project is based on the paper written by *David Card & Alan B. Krueger* in 1995 regarding research of the best-known predictions of standard economic theory that an increase in the minimum wage will lower employment of low-wage workers. Their result indicates that an increase of 10% in the minimum wage as a result a reduction between 1-3 % in teenage employment. 

- The main idea of our project is to reproduce their research by add our dataframe via Meta-Analysis

- In this work, we're going to implement the previous meta analysis with 3 most recent studies. 


-   requirements to re-run the obtained results are:

`R version 4.1.3`, `rmarkdown 2.14`, `tidyverse 1.3.1`, `stargazer 5.2.3`, `rcompanion 2.4.15`.

## Meta-Analysis

- A meta-analysis is a statistical analysis that combines the results of multiple scientific studies. Meta-analyses can be performed when there are multiple scientific studies addressing the same question, with each individual study reporting measurements that are expected to have some degree of error. 

- The aim then is to use approaches from statistics to derive a pooled estimate closest to the unknown common truth based on how this error is perceived. Meta-analytic results are considered the most trustworthy source of evidence by the evidence-based medicine literature


## Data (1/3) 

- the professor give us the Data of the *Card and krueger's Meta-Ananlysis*, but in that table missing three variable: 

  - information about teenager sub-sample
  
  
  - square root of degree of freedom 
  
  
  - logarithm of square root of degree of freedom
  

- we would be able to calculate the last two, but also reading the paper of the others author we couldn't find enough information about teenager sub-sample. 


- The original study includes 15 observations of 14 variables by year 1992.


## Data (2/3)

- our implementation concern:

    - J*inlan Ni , Guangxin Wang & Xianguo Yao*, "Impact of Minimum Wages on Employment", **2011**
    
    - *Majchrowska and Zolkiew*, "The Impact of the National Minimum Wage on Employment", **2012**
    
    - *Bewley et al.*, "The Impact of the National Minimum Wage on Employment", **2015**
    
- Below we will conduct two regression models which present by graph and table, first we'll use just the previous fifteen studies to reproduce the Card and Krueger's M-A, then we'll implement with our data and we'll see if the study keeps its validity


## Data (3/3)

### **t_stat**
```{r, echo=FALSE}
#kable(cbind(dt, dt, dt), booktabs = T) %>%
#  kable_styling(latex_options = c("striped", "scale_down"))
summary(dt$t_stat)
```
### **coef**
```{r, echo=FALSE}
summary(dt$coef)
```
### **df**
```{r, echo=FALSE}
summary(dt$df)
```


## procedure

- Now we're going to show our reproduction of the *Card and Krueger* study and then we'll compare their result with the same study implemented with our implementation. 

- We followed step by step their analysis, the first figure shows us the correlation between t_stat and logarithm of square root of degree of freedom.

- As you could see our result are consistent with the previuos Meta-Analysis. 


## Relation of Estimated t-Ratio to Sample Size (1/2)

-Graph Explanation: In the below graph we can see that with big samples(12,3,4,9,15) given the same effect size has T-Statistics less than 2, whereas smaller sample size somehow have just above 2(1,4,6,2).

```{r, warning = F, message = F, echo = F, fig.width = 6, fig.height = 4}
fig_1_old
```

## Relation of Estimated t-Ratio to Sample Size (2/2)

Graph Explanation: In the below graph we can see that the newly added data with bigger sample given the same effect has T-Statistics very close to 2.(16,17,18). It means it has more precises estimates. 

```{r, warning = F, message = F, echo = F, fig.width = 6, fig.height = 4}
fig_1_new
```


## Procedure
- In order to control the potential impact of other research characteristics on this dependence, we performed regressions with the logarithm of absolute t-ratio as the dependent variable selected independent variables were the logarithm of the square root of degrees of freedom, a number of explanatory variables in given research, and binary variables indicating whether the model specification in given research was logarithmic and if the autoregressive correction was implemented.

- As we could see the graph shows a negative relationship between the t ratios and the degrees of freedom. The coefficient on the square root of the degrees of freedom is quite far from 1, its theoretical expectation. The inclusion of additional explanatory variables does not change the sign of the coefficient or reduce its effect.

- Next, we will present the reproduced regressions in Table which gives us more information about the correlation. Furthermore, due to the fact the study number 7 is considered as biased data set, therefore we will also conduct table to analysis the result which excludes study number 7.

## Descreptive Regression Models (1/2)

- The striking pattern to notice that most of this studies have T-statistics just above 2 but in this case when they do regression the log t-stat on log degree of freedom instead of getting a slope of 1 they get a negative slope -0.94, This is deeply problematic if it was zero then also it was problematic but now it is negative, as seen in Relation of Estimated t-Ratio to Sample Size the previous graph cluster with big sample size given the same effect size which should have bigger t-statistics is actually getting a zero.
```{r, echo = F, results = 'asis', out.width = 6, out.height = 4}
cat(tbl1, sep = '\n')
```

## Descreptive Regression Models (2/2)

- The striking pattern to notice that when we added 3 new variables 16,17,18 and did regression the log t-stat on log degree of freedom instead of getting a slope of 1 we got a negative slope -0.40 which is better than -0.94.

```{r, echo = F, results = 'asis', out.width = 6, out.height = 4}
cat(tbl2, sep = '\n')
```

## is it t-statistics always 2?

-Another sort of meta-analysis compares the size of each study's coefficient to its estimated standard error. If the same statistical model remains true throughout time, there should be no systematic link between the estimated coefficients and their standard errors. However, if publication bias causes studies with t ratios greater than 2 to be published, we would expect to discover a positive association between the magnitude of the estimated employment effect and its standard errors. Assume that journals have a rule of only publishing papers with t ratios greater than 2, and that authors adjust their specifications (by shifting functional forms, changing the list of included variables, and so on) until they reach such a t ratio. Therefore we find many published paper with t-ratios equal to or just above 2.


## Histogram 

In statistics, the "normal distribution" is the most widely used distribution. A normal distribution has a histogram that is bell-shaped and symmetric around the mean. Kurtosis and skewness are words used to characterize deviations from normality. In the below graph we can see the positive skew this means that the right side's tail is longer than the left side's tail, and the majority of the values are to the somewhat left of the mean. This is mostly due to the fact that there is a very high upper restriction on intake but no lower limit.


```{r, echo=FALSE}
library(rcompanion)
plotNormalHistogram( dt$t_stat, prob = FALSE, col="indianred",
                     main = "Normal Distribution overlay on Histogram", linecol="black" )
```

## Procedure

- Now we're going to plot absolute value of the minimum-wage effect against their standard error. 

- This relation needs to looking these correlation, but also to see if the coefficients estimatedvare effectively 2 times their standard error (*to see these we'll implement our graphs with a line that it's 2 times the standard error*)

## Relation of Estimated Employment to Standard Error (1/2)

- Graph Explanation - This is another way of looking at the data where we have standard error of estimate and estimated elasticity effect, The graph plot out 2 times the standard error and you can see the incredible clustering of studies right above 2 times of the standard error (13,1,10,4,2,6). This is very unnatural, The most concerning thing to observe here is that studies with less standard error (13,1,11,8,14,5) are well powered studies. Probably this are most reliable studies.

```{r, warning = F, message = F, echo = F, fig.width = 6, fig.height = 4}
fig_2_old
```

## Relation of Estimated Employment to Standard Error (2/2)

- When we added new studies we can observe that (17,18) have less standard errror where has 16 have high standard error. Thus we can assume with this that studies (17,18) are more reliable then study 16.

```{r, warning = F, message = F, echo = F, fig.width = 6, fig.height = 4}
fig_2_new
```


## conclusion
Our findings are consistent with the original meta-analysis by Card and Krueger (1995), who argue that these countrintuitive results are caused by the fact that, when the available data are not too large, the norms used by researchers make them were able to find a significant negative correlation between minimum wages and their expected youth employment. However, due to its fragility, the significance decreases as more data is used. Our supplementary paper confirms that this trend in research bias is critical and still exists, with lower t-ratios for papers published after the 15 papers studied by Card and Kruger, even with larger data samples. 

In conclusion, there is strong evidence that research is often biased. Lack of self-awareness and excessive trust in existing literature can be misleading. 

## ended

\centering  Thank You

